### 2017-05-24 R/TravelSurvey.Rmd
Updates to TravelSurvey.Rmd

```{r TravelSurvey, eval = compute, fig.width = 10, echo = FALSE}
NHTS.ts <- readRDS(file = "~/GHI/R/data/NHTS.TravelSurvey.rds")
NHTS.df <- dplyr::left_join(NHTS.ts@person, NHTS.ts@trip, by = c("houseID","subjectID"))
NHTS.df <- within(NHTS.df, {
    duration <- ifelse(is.na(duration), 0, duration)
    mode <- factor(mode, levels = c("walk","cycle","other"))
})
```

@@

```{r plot1, eval = TRUE, fig.width = 20, echo = FALSE}
total <- NHTS.df %>% group_by(location) %>% summarise(mean = mean(duration), total = sum(duration), sdTotal = sd(duration), nTotal = n())

@@

p <- ggplot(NHTS.table2, aes(x = location, y = value, colour = mode))
p + geom_line(aes(group = ciMode))# + facet_grid(mode ~ . )

@@

```{r plot2, eval = TRUE, fig.width = 20, echo = FALSE}
p <- ggplot(subset(NHTS.df,!is.na(mode)), aes(x = location, y = duration, fill = location))
p + geom_boxplot(outlier.shape = NA) + ylim(0,60)
p + geom_violin(scale = "width" ) + ylim(0,60)
```

@@

```{r plot3, eval = TRUE, echo = FALSE, fig.width = 20, fig.asp = 1/phi}
p <- ggplot(subset(NHTS.df,!is.na(mode) & location == "5602"), aes(x = mode, y = duration, fill = mode))
p + geom_boxplot(outlier.shape = NA)
p + geom_violin(scale = "width", adjust = 4 )
```

>>>>

```{r TravelSurvey, eval = compute, fig.width = fig.width, echo = FALSE}
NHTS.ts <- readRDS(file = "~/GHI/R/data/NHTS.TravelSurvey.rds")
NHTS.df <- dplyr::left_join(NHTS.ts@person, NHTS.ts@trip, by = c("houseID","subjectID"))
NHTS.df <- within(NHTS.df, {
    duration <- ifelse(is.na(duration), 0, duration)
    mode <- factor(mode, levels = c("walk","cycle","other"))
})
```

@@

```{r plot1, eval = TRUE, fig.width = fig.width, echo = FALSE, fig.asp = 1/phi}
total <- NHTS.df %>% group_by(location) %>% summarise(mean = mean(duration), total = sum(duration), sdTotal = sd(duration), nTotal = n())

@@

p <- ggplot(NHTS.table2, aes(x = location, y = value, colour = mode))
p + geom_line(aes(group = ciMode)) + facet_grid(mode ~ . )

@@

```{r plot2, eval = TRUE, fig.width = fig.width, echo = FALSE, fig.asp = 1/phi}
p <- ggplot(subset(NHTS.df,!is.na(mode)), aes(x = location, y = duration, fill = location))
p + geom_boxplot(outlier.shape = NA) + ylim(0,60)
p + geom_violin(scale = "width" ) + ylim(0,60)
```

@@

```{r plot3, eval = TRUE, echo = FALSE, fig.width = fig.width, fig.asp = 1/phi}
p <- ggplot(subset(NHTS.df,!is.na(mode) & location == "5602"), aes(x = mode, y = duration, fill = mode))
p + geom_boxplot(outlier.shape = NA) + ylim(0,60)
p + geom_violin(scale = "width", adjust = 4 ) + ylim(0,60)
```
